Paper 2: Vitamin D

### 2017-09-19 doc/vitaminD.Rmd
finished vitamin D table shells analysis

@@

subchar_vitd_base <- tableone::CreateTableOne(
  vars = c("Age",
           "Sex",
           "Ethnicity",
           "BMI",
           "Waist",
           "eGFR",
           "ACR",
           "UrineCreatinine",
           "UrineMicroalbumin",
           "UrinaryCalcium",
           "UDBP",
           "udbpCrRatio",
           "VitaminD",
           "PTH",
           "MET",
           "Systolic",
           "Diastolic",
           "MeanArtPressure",
           "diet_milk",
           "diet_cal",
           "diet_supp_cal",
           "diet_supp_vitd",
           "OralContraceptive",
           "dmStatus"),
  strata = c("vitdStatus"),
  data = dsBase,
  factorVars = c("Sex", "Ethnicity", "OralContraceptive", "dmStatus")
) %>% 
  print(nonnormal = c("UDBP",
                      "ACR",
                      "UrineMicroalbumin"),
        quote = FALSE,
        noSpaces = TRUE)
```

@@

subchar_vitd_base <- tableone::CreateTableOne(
  vars = c("Age",
           "Sex",
           "Ethnicity",
           "BMI",
           "Waist",
           "eGFR",
           "ACR",
           "UrineCreatinine",
           "UrineMicroalbumin",
           "UrinaryCalcium",
           "UDBP",
           "VitaminD",
           "PTH",
           "Systolic",
           "Diastolic",
           "MeanArtPressure",
           "diet_milk",
           "diet_cal",
           "diet_supp_cal",
           "diet_supp_vitd",
           "OralContraceptive",
           "dmStatus"),
  strata = c("fVN"),
  data = ds,
  factorVars = c("Sex", "Ethnicity", "OralContraceptive", "dmStatus")
) %>% 
  print(nonnormal = c("UDBP",
                      "ACR",
                      "UrineMicroalbumin"),
        quote = FALSE,
        noSpaces = TRUE)
```

@@

dsBase %>% 
  prep_mason_data() %>% 
  mason_glm(y = "VitaminD",
            x = "udbpCrRatio",
            covars = c("ageBase", "Sex", "Ethnicity", "MET", "BMI", "Season", "fDM")
            ) %>% 
  dplyr::filter(!term == "(Intercept)") %>%
  dplyr::mutate(p = round(p.value, 2),
    p = ifelse(p == "0", "<0.001", p),
    estCI = paste0(round(estimate, 2), " (",
                               round(conf.low, 2), ", ",
                               round(conf.high, 2), ")")) %>% 
  dplyr::select(Yterms, Xterms, term, estCI, p) %>% 
  # tidyr::spread(Yterms, estCI) %>%
  pander::pander()

@@

PTH

@@

@@

dsComplete %>% 
  plot_progress(yvar = "VitaminD",
                ylab = "Serum 25(OH)D")
```

@@

gee_vitd_baseline <- ds %>% 
  prep_mason_data_kidney() %>% 
  mason_gee(y = c("VitaminD"),
            x = "udbpBase",
            covars = c("MonthsFromBaseline", "ageBase", "Sex", "Ethnicity", "BMI", "dmStatus", "Season"),
            intvar = "Season")

@@

plot_gee_results_vitd(gee_vitd_baseline,
                 yvars = c("uAlbumin:creatinine (mg/mmol)", 
                           "eGFR (ml/min/1.73m^2)"))
```

@@

gee <- ds %>% 
  prep_mason_data() %>% 
  mason_gee(y = c("VitaminD"),
            x = "udbpBase",
            covars = c("VN", "ageBase", "Sex", "Ethnicity", "BMI", "PTH", "fDM"))
  # dplyr::filter(!term == "(Intercept)") %>%
  # dplyr::select(Yterms, Xterms, term, estimate, p.value, conf.low, conf.high, std.error, sample.total)
  # knitr::kable()

# Predictor is UDBP at all time points ------------------------------

gee <- ds %>% 
  prep_mason_data() %>% 
  mason_gee(y = c("VitaminD"),
              x = "UDBP",
              covars = c("VN", "ageBase", "Sex", "Ethnicity", "BMI", "PTH", "fDM")) %>%
  dplyr::filter(!term == "(Intercept)") %>%
  dplyr::select(Yterms, Xterms, term, estimate, p.value, conf.low, conf.high, std.error, sample.total)
```

```{r gee_plot}

plot_gee_results_vitd(gee,
                 yvars = c("VitaminD"))
```

>>>>

```{r caption_setup}

## Include captions below using `captioner` package

fig_nums <- captioner::captioner(prefix = 'Figure')
supfig_nums <- captioner::captioner(prefix = 'Supplementary Figure')
tab_nums <- captioner::captioner(prefix = 'Table')
suptab_nums <- captioner::captioner(prefix = 'Supplementary Table')
```

@@

tab_nums("subchar_vitd_baseline", "Subject characteristics across vitamin D status at baseline")

subchar_vitd_base <- tableone::CreateTableOne(
  vars = c("Age",
           "Sex",
           "Ethnicity",
           "BMI",
           "Waist",
           "eGFR",
           "ACR",
           "UrineCreatinine",
           "UrineMicroalbumin",
           "UrinaryCalcium",
           "UDBP",
           "udbpCrRatio",
           "VitaminD",
           "PTH",
           "MET",
           "Systolic",
           "Diastolic",
           "MeanArtPressure",
           "diet_milk",
           "diet_cal",
           "diet_supp_cal",
           "diet_supp_vitd",
           "OralContraceptive",
           "dmStatus"),
  strata = c("vitdStatus"),
  data = dsBase,
  factorVars = c("Sex", "Ethnicity", "OralContraceptive", "dmStatus")
) %>% 
  print(nonnormal = c("UDBP",
                      "ACR",
                      "UrineMicroalbumin"),
        quote = FALSE,
        noSpaces = TRUE) %>% 
  knitr::kable()
```

@@

tab_nums("subchar_vitd", "Subject characteristics across visit numbers")

subchar_vitd_base <- tableone::CreateTableOne(
  vars = c("Age",
           "Sex",
           "Ethnicity",
           "BMI",
           "Waist",
           "MET",
           "VitaminD",
           "PTH",
           "UDBP",
           "udbpCrRatio",
           "Systolic",
           "Diastolic",
           "MeanArtPressure",
           "OralContraceptive",
           "dmStatus"),
  strata = c("fVN"),
  data = ds,
  factorVars = c("Sex", "Ethnicity", "OralContraceptive", "dmStatus")
) %>% 
  print(nonnormal = c("UDBP",
                      "udbpCrRatio"),
        quote = FALSE,
        noSpaces = TRUE)
```

@@

dsBase %>% 
  prep_mason_data() %>% 
  mason_glm(y = "VitaminD",
            x = "logudbpCrRatio",
            covars = c("ageBase", "Sex", "Ethnicity", "BMI", "MET", "fDM")
            ) %>% 
  dplyr::filter(!term == "(Intercept)") %>%
  dplyr::mutate(p = round(p.value, 2),
    p = ifelse(p == "0", "<0.001", p),
    estCI = paste0(round(estimate, 2), " (",
                               round(conf.low, 2), ", ",
                               round(conf.high, 2), ")")) %>% 
  dplyr::select(Yterms, Xterms, term, estCI, p) %>% 
  # tidyr::spread(Yterms, estCI) %>%
  pander::pander()

@@

#### Possible Effect Modifiers

@@

```{r vitd_season}

# Box plot of 25(OH)D in different seasons
dsBase %>% 
  box_plot("Season", "VitaminD", 
            "Seasons",
            "Serum 25(OH)D (nmol/L)")

# n
dsBase %>% 
  group_by(Season) %>% 
  summarise(n = n())

# ANOVA
anova <- aov(formula = VitaminD~Season, data = dsBase)
summary(anova)
TukeyHSD(anova)
rm(anova)
```

@@

dsComplete %>% 
  plot_progress(yvar = "VitaminD",
                ylab = "Serum 25(OH)D")

# ANOVA ------------------------------------------------------------

anova <- aov(formula = VitaminD~fVN, data = dsComplete)
summary(anova)
TukeyHSD(anova)
rm(anova)
```

@@

gee_vitd_baseline <- ds %>% 
  prep_mason_data_vitd() %>% 
  mason_gee(y = c("VitaminD", "PTH"),
            x = "udbpBase",
            covars = c("MonthsFromBaseline", "ageBase", "Sex", "Ethnicity", "MET", "BMI", "dmStatus", "Season"),
            intvar = "Season") %>% 
  mason::polish_renaming(rename_gee_vitd)

@@

gee_vitd_baseline <- ds %>% 
  prep_mason_data_vitd() %>% 
  mason_geeplot(y = c("VitaminD", "PTH"),
            x = "udbpBase",
            covars = c("MonthsFromBaseline", "ageBase", "Sex", "Ethnicity", "MET", "BMI", "dmStatus", "Season"),
            intvar = "Season") %>% 
  mason::polish_renaming(rename_gee_vitd)

plot_gee_results_vitd(gee_vitd_baseline,
                 yvars = c("Serum 25(OH)D (nmol/L)",
                           "PTH (pmol/L)"))

# Plot interaction ---------------------------------------------------

dsBase %>% 
  interac_plot(yvar = "PTH",
               intvar = "Season",
               ylab = "Parathyroid Hormone (pmol/L)") #Serum 25(OH)D (nmol/L) #Parathyroid Hormone (pmol/L)
```

@@

# Predictor is UDBP ----------------------------------------

gee_vitd <- ds %>% 
  prep_mason_data_vitd() %>% 
  mason_gee(y = c("VitaminD", "PTH"),
            x = "UDBP",
            covars = c("MonthsFromBaseline", "ageBase", "Sex", "Ethnicity", "MET", "BMI", "dmStatus", "Season"),
            intvar = "Season") %>% 
  mason::polish_renaming(rename_gee_vitd)

gee_vitd %>% 
  dplyr::filter(!term == "(Intercept)") %>% 
  dplyr::mutate(p = round(p.value, 2),
    p = ifelse(p == "0", "<0.001", p),
    estCI = paste0(round(estimate, 2), " (",
                               round(conf.low, 2), ", ",
                               round(conf.high, 2), ")")) %>% 
  dplyr::select(Yterms, Xterms, term, estCI, p) %>% 
  # tidyr::spread(Yterms, estCI) %>%
  pander::pander()

gee_vitd <- ds %>% 
  prep_mason_data_vitd() %>% 
  mason_geeplot(y = c("VitaminD", "PTH"),
            x = "UDBP",
            covars = c("MonthsFromBaseline", "ageBase", "Sex", "Ethnicity", "MET", "BMI", "dmStatus", "Season"),
            intvar = "Season") %>% 
  mason::polish_renaming(rename_gee_vitd)

plot_gee_results_vitd(gee_vitd,
                 yvars = c("Serum 25(OH)D (nmol/L)",
                           "PTH (pmol/L)"))

# Plot interaction ---------------------------------------------------

ds %>% 
  interac_plot(yvar = "VitaminD",
               intvar = "Season",
               ylab = "Serum 25(OH)D (nmol/L)")
```
